Deep Learning for Automatic Speech Recognition

### 2015-04-29 Paper/Paper.tex
Final changes
I think this is pretty much it

\section*{Introduction} \TODO{Intro sentence}

\paragraph{} Due to the complexity of the speech stream and massive amount of variations possible, the problem of automatic speech recognition is a difficult one to address. The human speech system is comprised of a series of continually moving articulators with highly variable targets across contexts. Systems need to deal with all of these contexts which can cause different acoustic representations for the same lexical target. One also needs to properly handle both physical and linguistic variation across speakers, differing degrees of fluency, large vocabulary sizes, and even background noise. All of these together demonstrate the need for a robust system that can account for such variance in its acoustic model.

\paragraph{} Deep learning approaches to ASR have seen recent success in addressing these issues, and appear to be the future means of constructing acoustic models. In this paper we examine two deep learning methods for automatic speech recognition: deep neural networks (DNNs) and convolutional neural networks (CNNs) based on the works of \cite{DBLP:journals/taslp/DahlYDA12} and  \cite{DBLP:journals/taslp/Abdel-HamidMJDPY14} respectively.

@@

\paragraph{} In this section we explore the work done in \cite{DBLP:journals/taslp/Abdel-HamidMJDPY14} with a convolutional neural network-hidden Markov model hybrid (CNN-HMM) for phone recognition on the TIMIT dataset and a large-vocabulary voice search task. The architecture used by \cite{DBLP:journals/taslp/Abdel-HamidMJDPY14} is heavily inspired by the use of CNNs for image recognition tasks. In this model, temporal variability is handled by the HMM, while convolutions occur along the frequency axis of the acoustic signal. We will begin by exploring the overall structure of the network, addressing the shape of the input and looking closely at the convolution and pooling plys. We will also look at the novel concept of limited weight sharing across the network. Pre-training is similar to that used in \cite{DBLP:journals/taslp/DahlYDA12}, so we will instead focus on the fine-tuning of parameters using the back-propagation algorithm. We will then transition into the results section where we will compare the performance of the CD-DNN-HMM with that of the CNN-HMM.

@@

\paragraph{} Over the past few years, convolutional neural networks have proven to be highly successful in image recognition tasks. Not only have they achieved the highest results on the MNIST character recognition dataset\cite{DBLP:journals/corr/abs-1003-0358}, but they've even proven to outstrip hand-crafted object recognition systems on the much more complex ImageNet dataset \cite{DBLP:conf/nips/KrizhevskySH12}. This success primarily originates from the networks ability to replicate lower-resolution features across the input space. They have also previously been used for speech recognition in \cite{hau2011exploring}, but without great success. There they claim that while CNNs look promising for ASR, just taking the same structure as one built for image recognition will not suffice. For example, in that work they used convolutions performed along the time axis. \cite{DBLP:journals/taslp/Abdel-HamidMJDPY14} attempts to address these concerns and instead design a CNN specifically for ASR.

@@

\begin{equation*}
	Q_{j} = \sigma (\sum_{i=1}^{I}O_{i}\star w_{i,j})
\end{equation*}
where $\star$ is the convolution operator, $O_{i}$ is the \textit{i}-th input feature map, and $w_{i,j}$ is the local weight matrix. For each unit in the convolution ply, all input units within the filter size are multiplied by their weights, summed, and passed through a non-linear function. Without padding the input with dummy values, the convolution operation would produce a lower-dimensional feature map where each dimension decreases by the filter size $F-1$. If this addition is done, there will be the same number of units in the input feature map as in that of the convolution ply.

@@

\paragraph{} Because the pooling plies have no weights, no learning occurs here. Despite this, errors need to be passed back to the convolution plies the draw from. Because max-pooling is used in this work, this process is fairly straightforward. Errors are only propagated backwards to the largest unit in the group of those pooled. Units with lower activations are left alone, and the weights are unaltered.

@@

\cite{DBLP:journals/taslp/Abdel-HamidMJDPY14} use just one convolution and pooling ply, and two 1000 unit, fully connected hidden layers in their experimental section. They Also make use of 150 feature maps for full weight sharing, and 80 feature maps for limited weight sharing. They do not explain their hardware resources or how long their training time took.

\TODO{Ryan verify CNN portion.)}

@@

\paragraph{} Based on what we've read, we believe that \cite{DBLP:journals/taslp/Abdel-HamidMJDPY14}'s convolutional neural network approach is better equipped to handle the speech recognition task. \cite{DBLP:journals/taslp/Abdel-HamidMJDPY14} have shown that better phoneme error rates can be obtained using fewer nodes and layers compared to the deep neural network approach of \cite{DBLP:journals/taslp/DahlYDA12}. Though, \cite{DBLP:conf/icassp/GravesMH13}'s recurrent neural network approach provides better performance over both suggesting that today's best of breed may easily be replaced tomorrow with something better.

>>>>

\section*{Introduction}

\paragraph{} Attempts to model certain aspects of human interaction with the physical world are some of the most interesting topics of our time. One such system is that of how we process speech. Due to the complexity of the speech stream and massive amount of variations possible, the problem of automatic speech recognition is a difficult one to address. The human speech system is comprised of a series of continually moving articulators with highly variable targets across contexts. Systems need to deal with all of these contexts which can result in different acoustic representations for the same lexical target. One also needs to properly handle both physical and linguistic variation across speakers, differing degrees of fluency, large vocabulary sizes, and even background noise. All of these together demonstrate the need for a robust system that can account for such variance in its acoustic model.

\paragraph{} Deep learning approaches to ASR have seen recent success in addressing these issues, and appear to be the future means of constructing acoustic models. In this paper we examine two deep learning methods for automatic speech recognition: Deep Neural Networks (DNNs) and Convolutional Neural Networks (CNNs) based on the works of \cite{DBLP:journals/taslp/DahlYDA12} and  \cite{DBLP:journals/taslp/Abdel-HamidMJDPY14} respectively.

@@

\paragraph{} In this section we explore the work done in \cite{DBLP:journals/taslp/Abdel-HamidMJDPY14} with a Convolutional Neural Network-hidden Markov model hybrid (CNN-HMM) for phone recognition on the TIMIT dataset and a large-vocabulary voice search task. The architecture used by \cite{DBLP:journals/taslp/Abdel-HamidMJDPY14} is heavily inspired by the use of CNNs for image recognition tasks. In this model, temporal variability is handled by the HMM, while convolutions occur along the frequency axis of the acoustic signal. We will begin by exploring the overall structure of the network, addressing the shape of the input and looking closely at the convolution and pooling plys. We will also look at the novel concept of limited weight sharing across the network. Pre-training is similar to that used in \cite{DBLP:journals/taslp/DahlYDA12}, so we will instead focus on the fine-tuning of parameters using the back-propagation algorithm. We will then transition into the results section where we will compare the performance of the CD-DNN-HMM with that of the CNN-HMM.

@@

\paragraph{} Over the past few years, Convolutional Neural Networks have proven to be highly successful in image recognition tasks. Not only have they achieved the highest results on the MNIST character recognition dataset\cite{DBLP:journals/corr/abs-1003-0358}, but they've even proven to outstrip hand-crafted object recognition systems on the much more complex ImageNet dataset \cite{DBLP:conf/nips/KrizhevskySH12}. This success primarily originates from the networks ability to replicate lower-resolution features across the input space. They have also previously been used for speech recognition in \cite{hau2011exploring}, but without great success. There they claim that while CNNs look promising for ASR, just taking the same structure as one built for image recognition will not suffice. For example, in that work they used convolutions performed along the time axis. \cite{DBLP:journals/taslp/Abdel-HamidMJDPY14} attempts to address these concerns and instead design a CNN specifically for ASR.

@@

\begin{equation*}
	Q_{j} = \sigma \left(\sum_{i=1}^{I}O_{i}\star w_{i,j}\right)
\end{equation*}
where $\star$ is the convolution operator, $O_{i}$ is the \textit{i}-th input feature map, and $w_{i,j}$ is the local weight matrix. For each unit in the convolution ply, all input units within the filter size are multiplied by their weights, summed, and passed through a non-linear function. Without padding the input with dummy values, the convolution operation would produce a lower-dimensional feature map where each dimension decreases by the filter size $F-1$. If this addition is done, there will be the same number of units in the input feature map as in that of the convolution ply.

@@

\paragraph{} Because the pooling plies have no associated weights, no learning occurs here. Despite this, errors need to be passed back to the convolution plies the draw from. Because max-pooling is used in this work, this process is fairly straightforward. Errors are only propagated backwards to the largest unit in the group of those pooled. Units with lower activations are left alone, and the weights are unaltered.

@@

\cite{DBLP:journals/taslp/Abdel-HamidMJDPY14} use just one convolution and pooling ply, and two 1000 unit, fully connected hidden layers in their experimental section. They also make use of 150 feature maps for full weight sharing, and 80 feature maps for limited weight sharing. As mentioned above, they do see some slight improvements in the LWS scheme. They do not explain their hardware resources or how long their training time took. Yet for a little perspective, in \cite{hau2011exploring} they used a somewhat similarly structured CNN which required less than a day to train. There's is less complicated than the one present in \cite{DBLP:journals/taslp/Abdel-HamidMJDPY14}, so slightly longer training times would not be surprising.

@@

\paragraph{} Based on what we've read, we believe that \cite{DBLP:journals/taslp/Abdel-HamidMJDPY14}'s Convolutional Neural Network approach is better equipped to handle the speech recognition task. \cite{DBLP:journals/taslp/Abdel-HamidMJDPY14} have shown that better phoneme error rates can be obtained using fewer nodes and layers compared to the Deep Neural Network approach of \cite{DBLP:journals/taslp/DahlYDA12}. Though, \cite{DBLP:conf/icassp/GravesMH13}'s Recurrent Neural Network approach provides better performance over both suggesting that today's best of breed may easily be replaced tomorrow with something better.
